Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/appendix.tex
removing (m)(r) for lemma 3
replacing omega with top

\equalMeet*
\begin{proof}
  For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  &\left(\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\right)(m)(r)\\
  =&(\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}})(m)(r)\\
  =&(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
  =&(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
  =&\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
  =&\left(\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
  \end{equation}
  \otodo{Where do we mention $\backEq$ in this lemma?}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
  \end{align*}
\end{proof}

@@

We will denote the top element in the environment lattice as
$\Omega=\lambda d\,.\,\topcc$.
\otodo{I've been using $\top_\textsf{Env}$ for clarity.}

@@

Additionally, for a path $p=[\startmain,\,\dots]$ and a fact $d\in D$, we will denote the lattice element that is mapped to $d$ according to the flow functions of path $p$ as follows:
\begin{equation}
  \mpd=\menv(p)(\Omega)(d)\,.
\end{equation}

@@

  Observe that
  \begin{align*}
    \mppd
    &=\menv(p')(\Omega)(d)\\
    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\Omega)(d)\\
    &=\menv(e_k)\left(\menv(p)(\Omega)\right)(d)\,.
  \end{align*}

As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equation. For an edge $(n_1,\,n_2)\in E^*$ an environment $\textsf{env}$ that maps $D$ to $L$, and a fact $d\in D$,
\begin{align}\label{eq:envTransToEdgeFnEdge}
  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
\end{align}  
Then, according to~\eqref{eq:envTransToEdgeFnEdge},\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\Omega)\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\Omega)(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

@@

\sound*
\begin{proof}
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{align*}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\Omega)(d')(r)\ne\top_T\right\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
\end{align*}
  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then for any $r\in R$, $\mpd(r)\ne\top_T$. 
  Since $\mpd(r)$ is a non-empty set that is contained in $\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)$, it follows that $$\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)\ne\top_T.$$ Therefore, $d\in \backCC(\resultIDE(\transCC_R(P)))(n)$.
\end{proof}

@@

  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\Omega)(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)\,.\qedhere
  \end{align*}
\end{proof}

>>>>

\equalMeet*
\begin{proof}
\begin{align*}
  &\denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}\\
  =&\denote{\setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}}\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap(I(r)\cup I'(r))\cup U(r)\cup U'(r)\\
  =&\lambda m\,.\,\lambda r\,.\,(m(r)\cap I(r))\cup U(r)\cup(m(r)\cap I'(r))\cup U'(r)\\
  =&\lambda m\,.\,\lambda r\,.\,\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)\\
  =&\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.\qedhere
\end{align*}
\end{proof}

@@

\precision*
\begin{proof}
    \otodo{It's Section 3.2.}
    \mtodo{Section 3.2 talks about the IFDS algorithm, but it doesn't explicitly say how the result of an IFDS analysis looks like and doesn't introduce the notation $\resultIFDS$.}
  Let $P$ be an IFDS problem. Recall from Section~\ref{sec:ideToIfds} that the result of an IFDS analysis $\resultIFDS(P)$ maps supergraph
  nodes $n\in N^*$ to sets of data-flow facts $\delta\in2^D$. Specifically,
  \begin{equation}
    \resultIFDS(P)=\lambda n\,.\,\mvp F(n)\,.
  \end{equation}
  \otodo{Where do we mention $\backEq$ in this lemma?}
  The transformation $\backCC$ is the same as $\backEq$, except that it can remove data-flow facts from the result:
  \begin{align*}
    \backCC\left(\resultIDE(\transCC_R(P))\right)(n)
    &=\left(\lambda n'\,.\,\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\right)(n)\\
    &=\left\{d\,|\,\forall r\in R\,.\,\resultIDE(\transCC_R(P))(n')(d)(r)\ne\top_T\right\}\\
    &\subseteq\left\{d\,|\,\resultIDE(\transCC_R(P))(n)(d)\ne\topcc\right\}\\
    &=\backEq\left(\resultIDE(\transCC_R(P))(n)\right).\qedhere
  \end{align*}
\end{proof}

@@

As previously we will denote the top element in the environment lattice as
$\top_\textsf{Env}$.
\otodo{I've been using $\top_\textsf{Env}$ for clarity.}

@@

Additionally, for a path $p=[\startmain,\,\dots]$ and a fact $d\in D$, we will denote the lattice element that is mapped to $d$ according to the flow functions of path $p$ as follows:
\begin{equation}
  \mpd=\menv(p)(\top_\textsf{Env})(d)\,.
\end{equation}

@@

  Observe that
  \begin{align*}
    \mppd
    &=\menv(p')(\top_\textsf{Env})(d)\\
    &=\left(\menv(e_k)\circ\menv(e_{k-1})\circ\ldots\circ\menv(e_1)\right)(\top_\textsf{Env})(d)\\
    &=\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)\,.
  \end{align*}

As shown in~Sagiv et al.~\cite{sagiv1996precise}, the relationship between environment transformers and edge functions can be described with the following equation. For an edge $(n_1,\,n_2)\in E^*$ an environment $\textsf{env}$ that maps $D$ to $L$, and a fact $d\in D$,
\begin{align}\label{eq:envTransToEdgeFnEdge}
  \menv&((n_1,\,n_2))(\textsf{env})(d)\notag\\
  &=\edgefn((n_1,\,\Lambda),\,(n_2,\,d))(\top)\sqcap\bigsqcap_{d'\in D}\edgefn((n_1,\,d'),\,(n_2,\,d))(\textsf{env}(d'))\,.
\end{align}  
Then, according to~\eqref{eq:envTransToEdgeFnEdge},\mtodo{Is it okay that in~\eqref{eq:envTransToEdgeFnEdge}, we use $\edgefn$, and below we use $\ccedgefn R$?}
  \begin{align*}
    &\menv(e_k)\left(\menv(p)(\top_\textsf{Env})\right)(d)(r)\\
      =&\bigg(\ccedgefn R((n_{k-1},\,\Lambda),\,(n_k,\,d))(\topcc)\sqcap\\
       &\bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))\bigg)(r)\\
      \supseteq&
        \bigsqcap_{d'\in D}\ccedgefn R((n_{k-1},\,d'),\,(n_k,\,d))(\menv(p)(\top_\textsf{Env})(d'))(r)\\
      \supseteq&\,\ccedgefn R((n_{k-1},\,d_{k-1}),\,(n_k,\,d))(\mpdkm)(r)\,.
  \end{align*}
  Therefore, 
  \begin{equation}\label{eq:musubset}
    \efek\subseteq\mppd(r)\,.
  \end{equation}

@@

\sound*
\begin{proof}
According to~\eqref{eq:ideresult}, we can rewrite~\eqref{eq:transCcDef} as
\begin{align*}\label{eq:transCcResultCc}
  \backCC(\resultIDE(\transCC_R(P)))(n)
  &=\{d'\,|\,\forall r\in R\,.\,\mvp{\textsf{Env}}(n,\,d'))(r)\ne\top_T\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\menv(q)(\top_\textsf{Env})(d')(r)\ne\top_T\right\}\\
  &=\left\{d'\,|\,\forall r\in R\,.\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d'}(r)\ne\top_T\right\}.
\end{align*}
  According to~Lemma~\ref{lem:sound3}, since $d\in M_F(p)(\varnothing)$, then for any $r\in R$, $\mpd(r)\ne\top_T$. 
  Since $\mpd(r)$ is a non-empty set that is contained in $\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)$, it follows that $$\bigsqcap_{q\in\textsf{VP}(n)}\mpddef q {d}(r)\ne\top_T.$$ Therefore, $d\in \backCC(\resultIDE(\transCC_R(P)))(n)$.
\end{proof}

@@

  According to~\eqref{eq:ideresult}, \eqref{eq:mvpdef}, and~\eqref{eq:envTransToEdgeFnEdge},
  \begin{align}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\mvp{\textsf{Env}}(n,\,d)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}M_\textsf{Env}(q)(\top_\textsf{Env})(d)\right)(r)\notag\\
    &=\left(\bigsqcap_{q\in\ivp(n)}\bigsqcap_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)\right)(r)\notag\\
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn S(q')(\topcc)(r)\,.\label{eq:resultThroughEdgefn}
  \end{align}
  Then from Lemma~\ref{lem:recindepedgefn},
  \begin{align*}
    \resultIDE\left(\transCC_S(P)\right)(n)(d)(r)
    &=\bigcup_{q\in\ivp(n)}\bigcup_{q'\in\mathsf{RP}(q,\,d)}\ccedgefn{\{r\}}(q')(\topcc)(r)\\
    &=\resultIDE\left(\transCC_{\{r\}}(P)\right)(n)(d)(r)\,.\qedhere
  \end{align*}
\end{proof}
